\documentclass{beamer}

\usepackage[utf8]{inputenc}

\title{Intro to Competitive Programming}
\author{David Piper}
\institute{Nashville Computer Science and Algorithms Meetup Group}
\date{September 19, 2020}

\begin{document}

\frame{\titlepage}

\begin{frame}
  \frametitle{What is Competitive Programming?}
  Competitive Programming is a type of contest where the goal is to produce
  correct algorithms to Computer Science problems with known solutions as quickly
  as possible.
\end{frame}

\begin{frame}
  \frametitle{Types of Competiive Programming Events}
  \begin{itemize}
    \item International Olympiad in Informatics (IOI)
    \item ACM International Collegiate Programming Contest (ICPC)
    \item Online Contests for Adult such as Topcoder
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Distinguishing Charactersistics}
  \begin{itemize}
    \item Timed competitions
    \item Algorithm design
    \item Correctness of algorithms emphasized
    \item Can write tests to trip up other contestants
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Why it is important for engineers?}
  \begin{itemize}
    \item Helps teach how to work using timeboxing
    \item Helps teach innovation
    \item Keeps coding interview skills fresh
    \item Helps improve testing and debugging skills
    \item Teaches you to identify hard problems vs solvable ones
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Why it is important for academics?}
  \begin{itemize}
    \item Great as a teaching tool
    \item Good way to practice algorithm design techniques
    \item Can be used to review formal methods
    \item Provides a framework for thinking about algorithm problems
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Types of problems}
  \begin{itemize}
    \item Sorting and Searching
    \item Dynamic Programming
    \item Graph Algorithms
    \item Range Queries
    \item Tree Algorithms
    \item Mathematics
    \item String Algorithms
    \item Other Advanced Problems
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{References and additional resources}
  \begin{itemize}
    \item [1]Thomas H. Cormen, Charles E. Leiserson, Ronald L. Rivest, and Clifford Stein. 2009. Introduction to Algorithms, 3rd Edition (3rd Edition ed.). The MIT Press, Cambridge, Mass.
    \item [2]Steven Halim. 2013. Competitive Programming 3 (Third Edition ed.). lulu.
    \item [3]Antti Laaksonen. CSES - CSES Problem Set - Tasks. Retrieved September 19, 2020 from \url{https://cses.fi/problemset}
  \end{itemize}
\end{frame}

\end{document}